cardinalR: Generating interesting high-dimensional data structures

### 2025-04-30 paper-cardinalR.Rmd
Updated scurve_tb
Added pyramid_tb

```{r}
pyramid_tb <- tibble(fun = c("gen_pyr",
                             "gen_pyrrect",
                             "gen_pyrtri",
                             "gen_pyrstar",
                             "gen_pyrholes"), 
                        exp = c("",
                                "",
                                "",
                                "",
                                ""))
```

@@

```{r}
scurve_tb <- tibble(fun = c("gen_scurve",
                            "gen_scurvehole"), 
                        exp = c("",
                                ""))
```

>>>>

```{r}
pyramid_tb <- tibble(fun = c("gen_pyrrect",
                             "gen_pyrtri",
                             "gen_pyrstar",
                             "gen_pyrholes"), 
                        exp = c("Generate a pyramid with a rectangular base, with the option of a sharp or blunted apex.",
                                "Generate a pyramid with a triangular base, with the option of a sharp or blunted apex.",
                                "Generate a pyramid with a star-shape base, with the option of a sharp or blunted apex.",
                                "Generate a pyramid with triangular pyramid shaped holes."))
```

@@

```{r}
scurve_tb <- tibble(fun = c("gen_scurve",
                            "gen_scurvehole"), 
                        exp = c("Generate a S-curve.",
                                "Generate a S-curve with a hole."))
```
